\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections

\begin{figure}[h]
\centering
\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
\label{fig:fem_cv}
\end{figure}

@@

\begin{figure}[h] 
\centering
\includegraphics[width=.5\textwidth]{./Pics/element_n.png}
\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements. The velocity and pressure are associated to the element corners and the mid-points as described in fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise.}
\label{fig:fem_elem}
\end{figure}

@@

\begin{figure}[h]
\makebox[\textwidth]{%
\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_perm}%
\hfill    
\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_mesh}%
}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\includegraphics[width=0.5\textwidth]{./Pics/2b2_P1DGP2_plot}%
}%
\caption{A simple test-case of a square region with four subregions. The permeability contrast is constant. The mesh is unstructured but fixed. After the injection of fluid $1$ at a velocity of u = 1, the velocity magnitude drops to zero. The main finger starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary. The mechanism that still drives the phenomenon is the pressure difference and the tip-splitting pattern can be more profound. }
\label{fig:square}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[MR1 fixed mesh start aspect ratio 2]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_1.png}
}%
\subfigure[MR1 fixed mesh end aspect ratio 2]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.png}
}\\
\end{center}
\caption{In this tes-case fixed and unstructured mesh is used. The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious. Simulation time step increases from left (a) to right (b) and from t=250(start) to t=3000(end).}
\label{fig:testcase}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[The $P_{1}DGP_{2}$ element type]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics/P1DG-P2_element_type}
}%
\subfigure[The map of permeabilities]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics/4r_po_adapt_fine_125_mesh}
}\\
\end{center}
\caption{(a) represents the element type of $P_{1}DGP_{2}$ as well as where each of the parameters is located and calculated on the element type. (b) describes the permeability map as this is introduced throught a python script during the set-up of simulations. In general, the main body of the formation is the blue area that is fully saturated with fluid $2$. Above the main (blue colored) area there are two layers - formations of different absolute permeabilities while in the main body there is a also a square shaped red coloured area where the two fluids exist in 50-50 phase ratio. All those ratios as well as the values of the permeabilities can be changes any time according to the data that are provided.   }
\label{fig:elem_type_perm_map}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[MR1 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.png}
}%
\subfigure[MR10 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.png}
}\\
\subfigure[MR1 fixed mesh middle]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.png}
}%
\subfigure[MR10 fixed mesh middle]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.png}
}\\
\subfigure[MR1 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.png}
}\\
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.png}
}\\
\end{center}
\caption{Comparing MR1 and MR10 cases using fixed mesh. Simulation time step increases from top to bottom and from t=100(start) to t=3000(end).}
\label{fig:1testcase}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[MR10 fixed mesh start]{%
\label{fig:first}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.png}
}%
\subfigure[MR10 adapt mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.png}
}\\
\subfigure[MR10 fixed mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.png}
}%
\subfigure[MR10 adapt mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.png}
}\\
\subfigure[MR10 fixed mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.png}
}%
\subfigure[MR10 adapt mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.png}
}\\ 
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.png}
}\\
\subfigure[MR10 adapt mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.png}
}\\
\end{center}
\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h). When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time. }
\label{fig:2testcase}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
\label{fig:fem_cv}
\end{figure}

@@

\begin{figure}[h] 
\centering
\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements. The velocity and pressure are associated to the element corners and the mid-points as described in fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise.}
\label{fig:fem_elem}
\end{figure}

@@

\begin{figure}[h]
\makebox[\textwidth]{%
\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_perm.pdf}%
\hfill    
\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_mesh.pdf}%
}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\includegraphics[width=0.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}%
}%
\caption{A simple test-case of a square region with four subregions. The permeability contrast is constant. The mesh is unstructured but fixed. After the injection of fluid $1$ at a velocity of u = 1, the velocity magnitude drops to zero. The main finger starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary. The mechanism that still drives the phenomenon is the pressure difference and the tip-splitting pattern can be more profound. }
\label{fig:square}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[MR1 fixed mesh start aspect ratio 2]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_1.pdf}
}%
\subfigure[MR1 fixed mesh end aspect ratio 2]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}\\
\end{center}
\caption{In this tes-case fixed and unstructured mesh is used. The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious. Simulation time step increases from left (a) to right (b) and from t=250(start) to t=3000(end).}
\label{fig:testcase}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[The $P_{1}DGP_{2}$ element type]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics/P1DG-P2_element_type.pdf}
}%
\subfigure[The map of permeabilities]{%
\label{fig:}
\includegraphics[width=0.45\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
}\\
\end{center}
\caption{(a) represents the element type of $P_{1}DGP_{2}$ as well as where each of the parameters is located and calculated on the element type. (b) describes the permeability map as this is introduced throught a python script during the set-up of simulations. In general, the main body of the formation is the blue area that is fully saturated with fluid $2$. Above the main (blue colored) area there are two layers - formations of different absolute permeabilities while in the main body there is a also a square shaped red coloured area where the two fluids exist in 50-50 phase ratio. All those ratios as well as the values of the permeabilities can be changes any time according to the data that are provided.   }
\label{fig:elem_type_perm_map}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[MR1 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
}%
\subfigure[MR10 fixed mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
}\\
\subfigure[MR1 fixed mesh middle]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}
}%
\subfigure[MR10 fixed mesh middle]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}\\
\subfigure[MR1 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf}
}\\
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf}
}\\
\end{center}
\caption{Comparing MR1 and MR10 cases using fixed mesh. Simulation time step increases from top to bottom and from t=100(start) to t=3000(end).}
\label{fig:1testcase}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[MR10 fixed mesh start]{%
\label{fig:first}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}
}%
\subfigure[MR10 adapt mesh start]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
}\\
\subfigure[MR10 fixed mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}
}%
\subfigure[MR10 adapt mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
}\\
\subfigure[MR10 fixed mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}
}%
\subfigure[MR10 adapt mesh]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
}\\ 
\subfigure[MR10 fixed mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}
}\\
\subfigure[MR10 adapt mesh end]{%
\label{fig:}
\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
}\\
\end{center}
\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h). When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time. }
\label{fig:2testcase}
\end{figure}
